---
title: 'OzoneModel: one easy App for ozone level prediction'
author: "Alberto L Gallotti"
date: "5/17/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(dplyr)
library(kableExtra)
library(datasets)
```

## What's OzoneModel

This is a very quick introduction to "**OzoneModel**", a very straightforward App
to generate a model predicting atmospheric ozone levels, based on the observations
taken in the summer months of 1973.


## The dataset

The dataset on which the analyses are conducted is the *airquality dataset*, embedded in R. It consists of 6 columns which contain

- the ozone levels
- the measurments of 3 other variables influencing ozone levels, i.e. Solar radiation (lang), Wind speed (mph), Temperature (°F)
- the id for month (from May to September) and day

```{r, echo=FALSE}
kable(head(airquality,4))
```


## The commands

The App asks the operator to select with a slider the month or months to consider
in order to predict the model, and to check the boxes for at least 1 to all 3 predictors (Solar radiation, Wind speed and Temperature) to insert in the model

The app also generates a timeline graph showing the levels of ozone in the months
selected (NA values are represented as interruption in the timeline)

```{r, echo = FALSE, fig.height=3, fig.width=8}
airquality$Date<-paste(airquality$Day,airquality$Month,'1973', sep = '-')
airquality$Date<-as.Date(airquality$Date, format = '%d-%m-%Y')
gg<-ggplot(airquality, aes(x=Date, y=Ozone))+geom_line(color='green')+
      ylab('Ozone Levels')+theme_dark()
gg
```

## The model

Once selected the months to consider and which predictor/predictors to use in generating the linear model, the App returns the coefficients for the Intercept
and each predictor selected, after having trained a linear model to predict ozone levels.

In this example, we show the output for a model considering *Solar Radiation* and
*Temperature* in the months of August and September.

```{r, echo=FALSE, comment=''}
monthsconsidered<-c(8,9)
ozonedf<-filter(airquality,airquality$Month%in%monthsconsidered)
fit<-lm(Ozone~Solar.R+Temp, data = ozonedf)
fit$coef
```

